Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-16 ms.tex
I added a figure showing the time series with a wider src finding box that allows for pointing wander.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.

@@

>>>>

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
We obtained photometry for 5 nights with good weather on the \sha\ system.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_bias_flat.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time bias correction, flat field correction and aperture centroiding was done.
Note that the target, reference stars 2 and 3 have smaller deviations at 0.81 days.}\label{fig:secTseriesBiasFlat}
\end{centering}
\end{figure}

It turns out that the large flux excursions in Figure \ref{fig:secTseries} and \ref{fig:secTseriesBiasFlat} are due to some bumps pointing errors and so substantial fractions of flux fall outside the source apertures.
I solved this problem by increasing the size of the subarray box (from 10 pix width to 18 px) so that the source would be found even if it wanders.
This results in much smaller flux excursions, as seen in Figure \ref{fig:secTseriesWiderBox}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
Bias correction, flat field correction and aperture centroiding was done.
The aperture centering (2D Gaussian fits) was done with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
\end{centering}
\end{figure}
